### 2024-04-30 Paper/paper.tex
Updates from Overleaf

@@

    \begin{equation}
    \label{eq:forprofit}
    y_{ht} = \beta (forprofit_h \times post\_penalty_t) + \alpha_{h} + \delta_t + \epsilon_{ht}
    \end{equation}

@@

    To identify the causal effect of hospital type on hospital program response, I rely on several assumptions. First, I assume that executive teams are not determined endogenously when the programs were enacted. I investigate the validity of this assumption in Section \ref{sec:endog}. Second, I assume that no other unobserved changes occurred in 2012 that differentially impact the outcomes of different hospital types. Finally, I assume that, absent the program enactments, different hospital types would have had parallel trends in outcomes. While not directly testable, I investigate the presence of pre-trends using an event study specification:

    \begin{equation}
    \label{eq:es}
    y_{ht} = \sum_{j=2009}^{2010}\beta_j(hospitaltype_{h} \times \mathbf{1}\{y=j\}) + \sum_{j=2012}^{2015}\beta_j (hospitaltype_{h} \times \mathbf{1}\{y=j\}) + \alpha_{h} + \delta_t + \epsilon_{ht},
    \end{equation}

    \noindent  where the coefficients $\beta_j$ now capture the effect of having being a specific hospital type in a particular year, and $\beta_{2011}$ is normalized to zero. \textcolor{red}{(figure out how to shift this to synthetic difference in difference specification and talk about the differences across hospital types)}

@@

    \begin{equation}
    change_{ht} = \beta(everpenalized_{h} \times post\_2011)+ \alpha_h + \delta_t + \epsilon_{ht}.
    \end{equation}

@@

     \subsection{Readmissions and Mortality}

@@

    Finally, I plot estimated coefficients from Equation \ref{eq:es} in Figure \ref{fig:wa_eventstudy}. The result is consistent with clinical team hospitals having higher readmissions post-penalty. The magnitude of the effect in the years after the penalty began are still around .5, but range from .26 to .54 from 2012-2014. Further, there is no indication that having clinical experience on the executive team causes a reaction in readmissions prior to the penalty.

    \begin{figure}[ht!]
        \caption{Event Study Estimates, Readmission}
        \includegraphics[scale=.5]{Objects/read_es_graph.pdf}
        \label{fig:wa_eventstudy}
    \end{figure}

@@

    I investigate whether mortality rates seem to be driven by a pre-trend, or whether the effect of clinical experience on mortality rates differs across time after the penalty occurs. Event study estimates from Equation \ref{eq:es} for the weighted average mortality model is shown in Figure \ref{fig:wa_eventstudy_mort}. These estimates reveal that hospital teams with clinical experience do not differentially change mortality rates compared to non-clinical experience teams before or after the penalties begin.

    \begin{figure}[ht!]
        \caption{Event Study Estimates, Mortality}
        \includegraphics[scale=.5]{Objects/mort_es_graph.pdf}
        \label{fig:wa_eventstudy_mort}
    \end{figure}

>>>>

    \import{Tables}{stable_sample_sumstats.tex}

@@

    \begin{equation}
    \label{eq:forprofit}
    y_{ht} = \beta (for\_profit_h \times post\_penalty_t) + \alpha_{h} + \delta_t + \epsilon_{ht}
    \end{equation}

@@

    To identify the causal effect of hospital type on hospital program response, I rely on several assumptions. First, I assume that executive teams are not determined endogenously when the programs were enacted. I investigate the validity of this assumption in Section \ref{sec:endog}. Second, I assume that no other unobserved changes occurred in 2012 that differentially impact the outcomes of different hospital types. Finally, I assume that, absent the program enactments, different hospital types would have had parallel trends in outcomes.

@@

    \begin{equation}
    change_{ht} = \beta(ever\_penalized_{h} \times post\_2011)+ \alpha_h + \delta_t + \epsilon_{ht}.
    \end{equation}

@@

     \subsection{Readmission and Mortality Rates}

@@

    \subsubsection{Decomposition}

@@
